---
title: "RTG 2660: Evaluation 2022"
author: "Sabrina Gado & Lea Hildebrandt"
format: 
  pdf:
    toc: true
    code-fold: false
    code-summary: "Show the code"
    code-overflow: wrap
    self-contained: true
execute:
  echo: false
editor: visual
---

# RTG 2660 Approach-Avoidance

## First-year evaluation

A survey was created and distributed in September 2022 by the RTG coordinator and PhD representatives, assessing how satisfied the PhD researchers were with the first year of their PhDs within the RTG. Questions spanned both broader RTG-related topics (atmosphere, organization etc.) and teaching.

```{r setup}
#| output: false
 
# load packages
library(tidyverse)
# install.packages("devtools")
remotes::install_github("rubenarslan/codebook")
# library(codebook)
library(labelled)
library(likert)
```

```{r prep-data}
#| output: false

# load data
 evals <- read_delim("~/UniWü/RTG2660/RTG_Statistics/Evaluation22/RTG_Eval/data_rtg2660_eval_ss22.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE) %>%
 filter(!is.na(AC01_01))

 # add items as labels and remove from data
 eval_labels <- evals[1,]
 eval_labels_list <- eval_labels %>% as.list(.)
 evals <- evals[2:nrow(evals),]
 
 # change type of columns
 evals <- evals %>%  type_convert(.)

 #### add response labels 
 # helper functions
 add_likert_labels <- function(x) {
  val_labels(x) <- c("strongly disagree" = 1, 
                  "slightly disagree" = 2, 
                  "neutral" = 3,
                  "slightly agree" = 4,
                  "strongly agree" = 5,
                  "not applicable/no opinion" = -1,
                  "NA" = 9,
                  "NA" = -9)
  x
 }
  add_yn_labels <- function(x) {
  val_labels(x) <- c("yes" = 1, 
                  "no" = 2,
                  "NA" = 9)
  x
}
 add_waste_labels <- function(x) {
  val_labels(x) <- c("waste of time" = 1, 
                  "bad" = 2, 
                  "neutral" = 3,
                  "good" = 4,
                  "excellent" = 5,
                  "NA" = 9,
                  "NA" = -9)
  x
 }
  add_less_labels <- function(x) {
  val_labels(x) <- c("less" = 1, 
                  "slightly less" = 2, 
                  "neutral" = 3,
                  "slightly more" = 4,
                  "more" = 5,
                  "not applicable/no opinion" = -1,
                  "NA" = 9)
  x
 }

 
 evals <- evals %>% mutate(across(c(AC01_01:AC05_02, 
                                    CO01_01:CO05_01, 
                                    GE02_01:GE02_02,
                                    JR01_01:JR01_09,
                                    SQ01_01:SQ02_12,
                                    SV01_01:SV01_07,
                                    TE01_01:TE01_05,
                                    TE05_01:WC03_01,
                                    WC04_01, WC05_01, WC01_01),
                                    add_likert_labels),
                          across(GE06, add_yn_labels),
                          across(TE05_01, add_waste_labels),
                          across(AC05_01:AC05_02, add_less_labels))
 
  # add labels from second row
 var_label(evals) <- eval_labels_list
 
 
 #### function for plotting
 eval_plot <- function(data, labels, variables) {
    # capture expressions and create quosures
  cols <- enquos(variables)
  
    # get headers/items
  sub_labels <- labels %>% dplyr::select(!!!cols) %>% gsub(".*:","", .)
  
   sub_data <- data %>% 
     select(!!!cols) %>% 
     mutate(across(where(is_numeric),as_factor)) %>% 
     mutate(across(everything(), ~fct_recode(.x,
                                             NULL = "not applicable/no opinion",
                                             NULL = "NA"))) %>%
     
     # somehow likert plot doesn't work with labels? rename cols
     setNames(sub_labels)  %>% 
     # also requires data.frame
     as.data.frame(.)
   
   eval_plot <- plot(likert(items=sub_data), legend.position="bottom") +
     # theme(legend.key.size = unit(.1, 'cm')) +
     guides(fill=guide_legend(title=NULL)) +
     theme(legend.justification = "right")
   
   eval_plot
   
 }
```


This evaluation was filled in by `r nrow(evals)` PhD students of the RTG 2660. Approximately half of those were funded by the RTG, the other half is associated.

```{r associated}
#| warning: false

ggplot(evals, aes(x="", fill=factor(GE06))) +
  geom_bar(stat="count", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(values = c("#00AB9C", "#B98E45", "grey"), name = "Associated?", labels = c("yes", "funded", NA)) 
```

## General

We asked questions assessing both broader categories, such as the PhD researcher's general impressions of the RTG, as well as specific categories such as teaching.

In general, the PhD researchers are happy to be part of the RTG and would recommend the RTG to others

```{r plot-general}
#| warning: false

eval_plot(evals, eval_labels, GE02_01:GE02_02)
```

We also asked some open question for each category.

The general feedback is very broad. An important point is the wish that PIs should participate in the Jour Fixe. The PhDs also would like to have the animal research represented better.

> **General Feedback:**

```{r openq-general}
#| results: asis

evals %>%
  select(GE03_01) %>%
  filter(!is.na(GE03_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

> **Maintain:**

```{r openq-general-2}
#| results: asis

evals %>%
  select(GE04_01) %>%
  filter(!is.na(GE04_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Atmosphere

We asked the PhD researchers for their general impression of the atmosphere within the RTG.

The responses show that PhD researchers generally appreciate the atmosphere but would like to have more (non-scientific) events organized for informal encounters.  

It thus seems like the PhD researchers would like to have *more (leisure) events offered* by the RTG. (However, during the PhD Assembly, the time pressure was also mentioned as a reason not to attend too many events, which should be taken into account.)

```{r plot-atmosphere}
#| warning: false

eval_plot(evals, eval_labels, AC01_01:AC01_03)

```

> **Atmosphere: I would wish for...**

```{r openq-atmosphere}
#| results: asis

evals %>%
  select(AC02_01) %>%
  filter(!is.na(AC02_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```



## Communication

The communication within the RTG is rated as being inclusive and support when conflicts arise is satisfying.

Public (science) communication is alright, but less personal information should be shared online.

The question arises whether the information on the website is meant here or e.g. the introductions on Twitter. *This is a point for further investigation and increased sensitivity.*

```{r plot-communication}
#| warning: false

ac2 <- eval_plot(evals, eval_labels, AC04_01:AC04_05)
ac2

ac3 <- eval_plot(evals, eval_labels, AC05_01:AC05_02)
ac3
```

> **Communication: I would wish for...**



```{r openq-communication}
#| results: asis

evals %>%
  select(AC06_01) %>%
  filter(!is.na(AC06_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Organization

PhD students are in general very satisfied with the organization and have the impression that they are heard. The time pressure is also addressed. However, it is a bit unclear to ~ half what exactly is expected from them to obtain their PhDs. *This is likely due to it depending on the RTG's requirements, the GSlS and of course the supervisor's expectancies.*  

```{r plot-organization}
#| warning: false

eval_plot(evals, eval_labels, CO01_01:CO05_01)

```

> **Organization: I would wish for...**

```{r openq-organization}
#| results: asis

evals %>%
  select(CO03_01) %>%
  filter(!is.na(CO03_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Skills


```{r plot-skillsoffer}
#| warning: false

eval_plot(evals, eval_labels, SQ01_01:SQ01_04)

```

```{r plot-skillsoutcome}
#| warning: false

eval_plot(evals, eval_labels, SQ02_01:SQ02_12)


```

> **Skills: I wish for...**

```{r openq-skills}
#| results: asis

evals %>%
  select(SQ03_01) %>%
  filter(!is.na(SQ03_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Supervision

```{r plot-jsupervision}
#| warning: false

eval_plot(evals, eval_labels, SV01_01:SV01_07)

```

> **Supervision: I wish for...**

```{r openq-supervision}
#| results: asis

evals %>%
  select(SV02_01) %>%
  filter(!is.na(SV02_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Jour Fixe

```{r plot-jourfixe}
#| warning: false

eval_plot(evals, eval_labels, JR01_01:JR01_09)

```

> **Jour Fixe: I wish for...**

```{r openq-jourfixe}
#| results: asis

evals %>%
  select(JR02_01) %>%
  filter(!is.na(JR02_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## Teaching

```{r plot-teaching}
#| warning: false

eval_plot(evals, eval_labels, TE01_01:TE01_05)

```

> **Teaching: I would wish for...**

```{r openq-teaching}
#| results: asis

evals %>%
  select(TE02_01) %>%
  filter(!is.na(TE02_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

> **Teaching: My favorite seminar sessions were the sessions by...**

```{r openq-teaching-favsem}
#| results: asis

evals %>%
  select(TE03_01, TE03_02) %>%
  filter(!is.na(TE03_01)) %>% 
  unite("combi", TE03_01:TE03_02, sep = ", because: ", remove = TRUE, na.rm = TRUE) %>%
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

> **Teaching: This seminar could be improved...**

```{r openq-teaching-badsem}
#| results: asis

evals %>%
  select(TE04_01, TE04_02) %>%
  filter(!is.na(TE04_01)) %>% 
   unite("combi", TE04_01:TE04_02, sep = ", particularly in terms of: ", remove = TRUE, na.rm = TRUE) %>%
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

```{r plot-teaching2}
#| warning: false

eval_plot(evals, eval_labels, TE05_01)

```

## Working Conditions

```{r plot-workcond}
#| warning: false

eval_plot(evals, eval_labels, c(WC03_01, WC04_01, WC05_01, WC01_01))


```

> **Office: I would like to change...**

```{r openq-wc-office}
#| results: asis

evals %>%
  select(WC02_01) %>%
  filter(!is.na(WC02_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

> **Home Office: I would like to change...**

```{r openq-wc-ho}
#| results: asis

evals %>%
  select(WC06_01) %>%
  filter(!is.na(WC06_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

> **Lab : I would like to change...**

```{r openq-wc-lab}
#| results: asis

evals %>%
  select(WC07_01) %>%
  filter(!is.na(WC07_01)) %>% 
  #mutate(AC02_01 = replace_na(AC02_01, "-")) %>% 
  unlist() %>%
  unname() %>% 
  { str_c("- ", ., "  \n") } %>%
  cat()

```

## 
